---
title: "10-import"
output: html_notebook
---

# Needed Libraries

```{r}
library(tidyverse)
library(dplyr)
library(janitor)
library(glue)
library(assertr)
library(lubridate)
library(RVerbalExpressions)
```
# Import Data

```{r}
library(readr)
gender_class<- read_csv("gender-classifier-DFE-791531.csv")
```

# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

Description:
A data frame with 20050 observations on 26 variables, each observation is one day.
Here is the official description: this data set was used to train a CrowdFlower AI gender predictor. Contributors were asked to simply view a Twitter profile and judge whether the user was a male, a female, or a brand (non-individual). The dataset contains more than 20,000 rows, each with a user name, a random tweet, account profile and image, location, and even link and sidebar color.

The problem: 
If one person tends to post more, then will this person retweet more? Any difference on tweet posts toward the gender or time?


2. Read in and check data
```{r data structure}
str(gender_class)
head(gender_class)
dim(gender_class)
summary(gender_class)
```

```{r check }
colnames(gender_class)[1] <- "unit_id"
colnames(gender_class)[2] <- "golden"
colnames(gender_class)[3] <- "unit_state"
colnames(gender_class)[4] <- "trusted_judgments"
colnames(gender_class)[5] <- "last_judgment_at"

head(gender_class)
```

```{r check NA}
for(col in names(gender_class)) {
  gender_class %>% 
    assert(not_na, col)
}

# Output shown that NA exists here for columns.
```


```{r check duplicate in ID}
length(unique(gender_class$unit_id)) 
# unique() keeps only unique elements, here the length is 20050 which is the same as we know from the data's description. Therefore, there is no duplicate in ID.
```

```{r check the data}
gender_class%>% # check the limit (based on description) for each variable 
  assert(in_set(c("TRUE", "FALSE")), golden)%>% 
  assert(in_set(c("finalized", "golden")), unit_state)%>%
  assert(in_set(c("male", "female","brand")), gender)%>%
  assert(within_bounds(0,1),`gender:confidence`) %>%
  assert(within_bounds(0,1),`profile_yn:confidence`)%>%
  assert(within_bounds(0,Inf),`fav_number`)%>%
  assert(within_bounds(0,Inf),`retweet_count`)%>%
  assert(within_bounds(0,Inf),`tweet_count`)
  
# According to the description, the variable gender contains one of male, female, or brand (for non-human profiles). However, here it has another type of records as "unknown".
```



2. Clean up the data. 

```{r clean the data}
# 0 in hex value should be having six digits, so here I changed it.
gender_class%>%
  mutate(sidebar_color = replace(sidebar_color, sidebar_color == "0", "000000"))
```

```{r clean the data}
# value for gender_gold is all NA.
length(is.na(gender_class$gender_gold) == TRUE)
# value for profile_yn_gold is all NA. Whether the profile y/n value is golden.
length(is.na(gender_class$profile_yn_gold) == TRUE)
# Here, we see that values are all NA for these two variables.
```

```{r clean the data}
# Here we try to replace replace unknown with NA under the variable of gender, since there is no label called "unknown" based on the description.
gender_class %>% 
  mutate(gender=ifelse(gender=="unknown",NA,gender))
```

```{r mutate a variable called duration}
new_gender_class <- gender_class%>%
  mutate(last_d = format(as.POSIXct(last_judgment_at,format='%m/%d/%y %H:%M'),format='%m/%d/%y'), first_d = format(as.POSIXct(created,format='%m/%d/%y %H:%M'),format='%m/%d/%y'))%>%
  mutate(duration = as.Date(last_d,"%m/%d/%y")- as.Date(first_d, "%m/%d/%y"))
```

